Vergleich von Cloud-Modellen

### 2015-03-22 Paper/content/10_references.tex

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

>>>>

\bibitem{vortragSAP}
Martin Heisig. "Public Cloud vs. Private Cloud: Cloud Computing - Wie die Industrie sich neuen Herausvorderungen stellt", Vortrag am Hasso-Plattner-Institut, Potsdam, 27.11.2014.

\bibitem{vortragFujitsu}
Karsten Beins. "Flexible options to make Cloud a viable choice for enterprise IT", Vortrag am Hasso-Plattner-Institut, Potsdam, 04.12.2014.

\bibitem{binnig2009}
Carsten Binnig, Donald Kossmann, Tim Kraska und Simon Loesing. "How is the Weather tomorrow?: Towards a Benchmark for the Cloud", Proceedings of the Second International Workshop on Testing Database Systems (DBTest '09), ACM, New York, NY, USA, 2009.

\bibitem{li2010}
Ang Li, Xiaowei Yang, Srikanth Kandula und Ming Zhang. "CloudCmp: Comparing Public Cloud Providers", Proceedings of the 10th ACM SIGCOMM conference on Internet measurement, ACM, 2010.

\bibitem{garg2011}
Saurabh Kumar Garg, Steven Versteeg und Rajkumar Buyya. "SMICloud: A Framework for Comparing and Ranking Cloud Services", Fourth IEEE International Conference on Utility and Cloud Computing (UCC), IEEE, 2011.

\bibitem{zhang2013}
Xiao Zhang, Feng WenXiong und Xiao Qin. "Performance Evaluation of Online Backup Cloud Storage", International Journal of Cloud Applications and Computing (IJCAC) 3.3 (20-33), 2013.

\bibitem{zenuni2014}
Xhemal Zenuni, Jaumin Ajdari, Florije Ismaili und Bujar Raufi. "Cloud Storage Providers: A Comparison Review and Evaluation", Proceedings of the 15th International Conference on Computer Systems and Technologies, ACM, 2014.
